Predicting Diabetes Based on Various Factors Using logistic Regression

### 2023-11-14 manuscript/manuscript.tex
Start of results section

>>>>

After completing our methods section, we can now move on to talk about the results of our model. Based on our logistic regression model, we now know that all of the predictors in the data set except skin thickness are important in order to predict whether a patient may have diabetes or not. With this information medical professionals will be able to ensure proper treatment to patients as they can use these predictors in order to tell if a patient may have diabetes even sooner than typical means. The model allows for medical professionals to use the model in order to further their research into diabetes and the various precursors.
